---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mfutils

<!-- badges: start -->
<!-- badges: end -->

The mfutils package is a collection of R functions that I frequently use for data analysis.
Most of these functions I have created myself, however some I have found on the interwebs (e.g., stack overflow), in which case I have also included the relevant attribution/url in the documentation.

These functions can be sorted into different categories:

- __general__ utilities for constructing and manipulating base R objects, such as character vectors and lists
- common __matrix__ operations
- __plotting__ (mostly ggplot2 enhancements)
- tools for implementing __representational similarity analysis (RSA)__, including spatial prewhitening and various distance measures
- convenience functions for working with __gifti__ objects from the `gifti` package (for surface fMRI data)
- as well as functions that enforce a standardized way to use __parcellation atlases__

Currently, I prefer to have all of these functions within a single package.
As this package becomes more developed, I may split off encapsulated sets of functions into separate packages.

## Installation

If for whatever reason you would like to install this package, you can do so with:

``` r
# install.packages("devtools")
devtools::install_github("mcfreund/mfutils")
```
